Percolation Analysis – Building a Package

### 2019-07-31 paper.Rmd
fixed mem_clust_by_r not found
-> wird als csv exportiert, dann wieder importiert. sinnig???

sNL_shape <- readOGR(dsn="shape_files/alle_Schnitt-Fundstellen.shp"

@@

source("R/mapping_clusters.v4.12.R")
mapClusters(data = data, shape = sNL_shape)

>>>>

sNL_shape <- readOGR(dsn="shape_files/alle_Schnitt-Fundstellen.shp")

@@

source("R/mapping_clusters.v4.12.R")
mapClusters(data = data, radius_values = 10, limit = 500, radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20, shape = sNL_shape)
